### 2020-08-15 thesis/thesis.tex
fix some refs todo
no dedication

\SetTitle{\huge{Integrating land use and land cover change simulations and connectivity modelling: a case study in the Montérégie region in southern Quebec}}%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%         Dedication                         %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \SetDedicationName{{Dedication}}%
% \SetDedicationText{}%
% \Dedication%

@@

%TODO mention bronwyn for parts of the code, Guillaume and Bronwyn for parts of the code and for providing LANDIS summary for out model inputs. + Yann and NRCAN.

>>>>

\SetTitle{\huge{Integrating land use and land cover change simulations and connectivity modelling: a case study in the Montérégie region in southern Québec}}%

@@

@@
